# [Model 1]


```{r}

# using https://www.kaggle.com/datasets/metmuseum/the-metropolitan-museum-of-art-open-access

df <- read.csv("~/Downloads/MetObjects.csv")
summary(df)

colSums(is.na(df)) # this dataset has been previously cleaned, no missing values 

highlightT <- df[df$Is.Highlight == TRUE,]

```


```{r}
library(ggplot2)
#table(df$Department)

ggplot(highlightT, aes(x = Department)) + 
  geom_bar() + theme_light() + theme(axis.text.x = element_text(angle = 45, size = 5, hjust=1))

```
Most of the artworks at the Met at Drawings and Prints. This makes sense becuase these are probably the easiest high medium to make! Photographs are also low effort to make and thus they are in high quantity. 

```{r}
ggplot(df, aes(x = Is.Highlight)) + 
  geom_bar() + theme_light()

```

```{r}
ggplot(df, aes(x = Is.Public.Domain)) + 
  geom_bar() + theme_light()
```

```{r}
library(OneR)

set.seed(5293)
n <- nrow(df)
train <- sample(n, .8*n)
train_dat <- df[train, ]
test_dat <- df[-train, ]

mod <- OneR(Is.Highlight ~ Classification + Country + Artist.Nationality + Artist.Display.Name + Object.Name + Department + Is.Public.Domain + Object.Date, data = train_dat)
#summary(mod)

#mean(predict(mod, train_dat) == train_dat$Is.Highlight)

#mean(predict(mod, test_dat) == test_dat$Is.Highlight)



```

The One Rule Model does not work for this task. The summary of the model is incredibly dense, and the "One Rule" chosen is in fact the name of the artist. For a datset of this size, it is almost impossible to interpret the model results because the model results are no better than me walking into the Met with a list of famous artists in my head. Van Gogh = Is.Highlight I would expect, and that is the case. 